---
format: html
execute: 
  echo: false
---

## 🧠 **Predictive Model Structure (Mathematical Form)**

Since we're predicting a binary outcome (`Survival_Status`), a **logistic regression model** is appropriate.

Let’s define the **model mathematically**:
$$
\text{logit}(P(Y = 1)) = \beta_0 + \beta_1 \cdot \text{Age} + \beta_2 \cdot \text{Gender} + \beta_3 \cdot \text{CancerType} + \beta_4 \cdot \text{Stage} + \beta_5 \cdot \text{DiagnosisTime}
$$ 


**Where:**

- \( Y = 1 \) if the patient is **Deceased**, \( Y = 0 \) otherwise  
- **logit(p)** is the **log-odds function**: log(p/1-p)  
- **Age** is a continuous numerical variable  
- **Gender**, **Cancer_Type**, and **Stage_at_Diagnosis** are **categorical variables**, internally converted to dummy variables by R  
- **Diagnosis_Date** represents the **date of diagnosis**, which may need to be transformed into a numeric format (e.g., years since 2010)

```{r}
#| warning: FALSE
#| echo: false
#| message: FALSE
library(readr)
library(dplyr)
library(broom)
library(kableExtra)
# Load your dataset
cancer_data_clean <- read_csv("cancer_data_cleaned_version.csv")
model_survival <- glm(Survival_Status == "Deceased" ~ Age + Gender + Cancer_Type +
                      Stage_at_Diagnosis + Diagnosis_Date, data = cancer_data_clean, family = binomial)
```

```{r}
tidy_survival <- tidy(model_survival, conf.int = TRUE)
```

```{r}
tidy_survival %>%
  select(term, estimate, conf.low, conf.high) %>%
  kable(caption = "Model Estimates with Confidence Intervals") %>%
  kable_styling()
```



